### 2021-07-23 paper2/appendix.tex
progress
Write a bit

>>>>

\subsection{Instructions for potential users}
The first question a potential user has to ask themselves is
whether the method is a good fit:
is the problem that the user faces one of strong spurious correlation
and is there non-spurious data available that has labels for the spurious variable?
To investigate the first part of the question,
the user should first try to train a standard neural network classifier
and observe the test-set performance.
Furthermore, one should check
whether the spurious variable can be removed with data augmentations alone.

to use the cFlow or cVAE variant of the method.
For initial experiments, we would recommend the cVAE model as it is quicker to train,
and will lead to shorter feedback cycles when validating the code.
If the computational budget allows it,
we would recommend switching to the cFlow model once cVAE is working
as it provides better guarantees regarding the retention of information from the input data.
